\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-02-02 paper.qmd
Add spin-brush with detour and try with liminal as well

## To draw with AIC
aic_plot <- ggplot(MSE_df |> dplyr::filter(data_type == "training") |> dplyr::filter(method == "UMAP"), aes(x = number_of_bins,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("Total number of bins")
## Effective number of bins along x-axis

mse_plot <- ggplot(MSE_df |> dplyr::filter(method == "UMAP"), aes(x = number_of_bins,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
   geom_vline(xintercept = 144, linetype="dashed", 
                color = "red", size=0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("Total number of bins")

@@

## To draw with AIC
aic_plot_lwd <- ggplot(MSE_df_lwd |> dplyr::filter(data_type == "training") |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_hex,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("benchmark value")
## Effective number of bins along x-axis

@@

## To draw with AIC
aic_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_point(data = error_df_lg |> dplyr::filter(method == "UMAP") |> filter(benchmark_rm_lg == 1.347), aes(x = benchmark_rm_lg,
                                       y = total_error
),
                                       color = "#e41a1c") +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("benchmark value")
## Effective number of bins along x-axis

mse_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_point(data = error_df_lg |> dplyr::filter(method == "UMAP") |> filter(benchmark_rm_lg == 1.347), aes(x = benchmark_rm_lg,
                                       y = total_mse
),
                                       color = "#e41a1c") +
  geom_line() +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("benchmark value")

@@

xtable(error_df, caption = "errors for different parameter combinations", label = "tbl-errordiffcomb") |>
  xtable2kable() |>
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = FALSE) |>
  row_spec(0, bold = TRUE) |>
  row_spec(7, bold=T, color = "red")
```

>>>>

## To draw with AIC
aic_plot <- ggplot(MSE_df |> dplyr::filter(data_type == "training") |> dplyr::filter(method == "UMAP"), aes(x = number_of_bins,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 144, linetype="dashed", 
                color = "red", size=0.5) +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("total number of bins")
## Effective number of bins along x-axis

mse_plot <- ggplot(MSE_df |> dplyr::filter(method == "UMAP"), aes(x = number_of_bins,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
   geom_vline(xintercept = 144, linetype="dashed", 
                color = "red", size=0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("total number of bins")

@@

## To draw with AIC
aic_plot_lwd <- ggplot(MSE_df_lwd |> dplyr::filter(data_type == "training") |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_hex,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 0.2, linetype="dashed", 
                color = "red", size=0.5) +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("benchmark value")
## Effective number of bins along x-axis

@@

## To draw with AIC
aic_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_vline(xintercept = 1.347, linetype="dashed", 
                color = "red", size=0.5) +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("benchmark value")
## Effective number of bins along x-axis

mse_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_vline(xintercept = 1.347, linetype="dashed", 
                color = "red", size=0.5) +
  geom_line() +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("benchmark value")

@@

kable(error_df, caption = "errors for different parameter combinations", label = "tbl-errordiffcomb") |>
  #xtable2kable() |>
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = FALSE) |>
  row_spec(0, bold = TRUE) |>
  row_spec(7, bold=T, color = "red")
```

### 2024-02-02 paper.tex
Add spin-brush with detour and try with liminal as well

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, frame hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrlr}
  \hline
\textbf{} & \textbf{n\_neighbors} & \textbf{min\_dist} & \textbf{metric} & \textbf{error (x 100) }\\ 
  \hline
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{5.00} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{355.97 }\\ 
  2 & 230.00 & 0.99 & cosine & 378.64 \\ 
\textcolor{red}{\textbf{\cellcolor{gray!6}{  3}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{30.00}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{0.30}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{cosine}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{386.35 }}}\\ 
   \hline
\end{tabular}
\caption{errors for different parameter combinations} 
\label{tbl-errordiffcomb}
\end{table}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, sharp corners, interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

\begin{table}[H]

\caption{errors for different parameter combinations}
\centering
\begin{tabular}[t]{r|r|l|r}
\hline
\textbf{n\_neighbors} & \textbf{min\_dist} & \textbf{metric} & \textbf{error (x 100)}\\
\hline
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{262.18}\\
\hline
15 & 0.99 & cosine & 279.49\\
\hline
\cellcolor{gray!6}{84} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{295.64}\\
\hline
5 & 0.30 & cosine & 303.90\\
\hline
\cellcolor{gray!6}{15} & \cellcolor{gray!6}{0.30} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{308.97}\\
\hline
84 & 0.30 & cosine & 319.59\\
\hline
\textcolor{red}{\textbf{\cellcolor{gray!6}{30}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{0.30}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{cosine}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{386.35}}}\\
\hline
\end{tabular}
\end{table}
